Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-28 finalReportPres.tex
Update finalReportPres
I added some slides to the final report.

\begin{frame}{Introduction}{}
 % \begin{center}
 %    \href{videos/smartRoboticCartIntroVideo.mp4}{\includegraphics[width=0.8\textwidth]{figs/img/finalPresVideoTitle.png}}
 %  \end{center}
\end{frame}

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{LARGE}
      Design a robotic cart that follows the user without line of sight (LoS) sensors
    \end{LARGE}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{LARGE}
      Utilize wireless radio frequency (RF) signal strength to locate and then follow the user
    \end{LARGE}
  \end{block}
\end{frame}

@@

\begin{frame}{Introduction}{Previous Work}
  \begin{block}{Existing Solution}
        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

\begin{frame}{Introduction}{Previous Work}
  \begin{block}{Existing Solution}
        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
    %     \caption{Shopping Support Robot}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

@@

\begin{frame}{Conclusions and Future Work}
  \begin{block}{Conclusions}
    \begin{itemize}
      \item The algorithm we implemented works the majority of the time
      \item Through tests and gathering data we were able iterate on our approach and tune the algorithms to function more reliably
      \item Our design is cost effective in comparison to other robotic carts
    \end{itemize}
  \end{block}
  \begin{block}{Future Work}
    \begin{itemize}
      \item Improve the localization algorithm for better angle estimation
      \item Test more reflector designs to see if the XBee signals can be more refined
      \item Implement obstacle detection and avoidance
      \item Multi-frequency radio modules to try to improve distance estimation
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}{Introduction}{}

\end{frame}

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
\end{frame}

@@

%\begin{frame}{Introduction}{Previous Work}
%  \begin{block}{Existing Solution}
%        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
%  \end{block}
%    % \begin{figure}[b]
%    %     \centering
%    %     \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
%    %     \caption{CompaRob}
%    %     %\label{fig:sysBlockDiag}
%    % \end{figure}
%\end{frame}
%
%%----------------------------------
%
%\begin{frame}{Introduction}{Previous Work}
%  \begin{block}{Existing Solution}
%        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
%  \end{block}
%    % \begin{figure}[b]
%    %     \centering
%    %     \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
%    %     \caption{Shopping Support Robot}
%    %     %\label{fig:sysBlockDiag}
%    % \end{figure}
%\end{frame}

%----------------------------------
\section{Literature Review}

\begin{frame}{Literature Review}{}

\end{frame}
%---------------------------
\section{System Identification Preliminaries}

\begin{frame}{System Identification Preliminaries}{}

\end{frame}

\begin{frame}{System Identification Preliminaries}{Examples}
  \begin{block}{}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
  \begin{block}{}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
\end{frame}
%-------------------------
\section{System Architecture}

\begin{frame}{System Architecture}{}

\end{frame}

\begin{frame}{System Architecture}{Subsystems}

\end{frame}

\begin{frame}{System Architecture}{Subsystems}

\end{frame}
%---------------------------
\section{System Modeling using Neural Networks}

\begin{frame}{Modeling using Neural Networks}{}

\end{frame}
%-------------------------
\section{Modeling Vehicle Subsystems}

\begin{frame}{Modeling Vehicle Subsystems}{}

\end{frame}

\begin{frame}{Modeling Vehicle Subsystems}{System Requirements}

\end{frame}
%-------------------------
\section{Validation and Testing}

\begin{frame}{Validation and Testing}{Experimental Setup}

\end{frame}

\begin{frame}{Transfer Function Modeling}{Steering System}

\end{frame}

\begin{frame}{Transfer Function Modeling}{Acceleration System}

\end{frame}

\begin{frame}{Transfer Function Modeling}{Brake System}

\end{frame}

\begin{frame}{Neural Network Modeling}{Steering System}

\end{frame}

\begin{frame}{Neural Network Modeling}{Acceleration System}

\end{frame}

\begin{frame}{Neural Network Modeling}{Brake System}

\end{frame}

@@

\begin{frame}{Conclusions and Future Work}
  \begin{block}{Conclusions}
    \begin{itemize}
      \item 
    \end{itemize}
  \end{block}
  \begin{block}{Future Work}
    \begin{itemize}
      \item 
    \end{itemize}
  \end{block}
\end{frame}
